Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2018-02-09 paper.tex
Update paper.tex

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{combination.png}
	\caption{Map of the natural ranges of wild relatives of three domesticated crops, overlayed with average annual temperature. The distribution of average annual temperature experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}

@@

As a species, domesticated crops are among our first and greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agronomic Revolution.
In this more nuanced and dynamic understanding of crop domestication, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.
\gmj{I let these final few sentences get a little more poetic than I normally would.  I think maybe I should reel them back in, or cut them.}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{temperature_plot.png}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature. The distribution of average annual temperature experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{boxplot.png}
	\caption{The distribution of average annual temperatures experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}

@@

Domesticated crops are among humanity's first and greatest inventions.
%As a species, domesticated crops are among our first and greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agronomic Revolution.
In this more nuanced and dynamic understanding of crop domestication, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.
\gmj{I let these final few sentences get a little more poetic than I normally would.  I think maybe I should reel them back in, or cut them.}
